% Relevance and what alternatives there are
\section{Introduction}

This cookbook presents a fully local pipeline for generating talking-head animations from static
images and arbitrary text, leveraging \gls{Zonos} for voice cloning and text-to-speech and
\gls{memo} for precise lip-synchronization. Designed to run entirely on your own hardware, this
application ensures data privacy, offline functionality, and the flexibility to customize every
component.

In today’s media landscape, immersive and personalized audiovisual content drives engagement across
educational platforms, virtual assistants, and marketing campaigns. By combining high-fidelity voice
cloning with accurate mouth animation, creators can produce dynamic videos without relying on cloud
services or external APIs. This guide walks you through setting up the environment, preparing your
data, and executing each stage of the pipeline, from extracting a speaker’s voice characteristics to
animating a still image’s mouth movements to match the synthesized speech.

At the core of this pipeline are two specialized tools: \gls{Zonos} and \gls{memo}. \gls{Zonos}
provides an end-to-end solution for voice cloning and speech synthesis, enabling you to input a
short audio sample and generate natural-sounding speech for any text. \gls{memo} handles the visual
side, mapping the generated audio waveform onto a static image to produce lipid-accurate mouth
movements. You’ll find detailed instructions for installing dependencies, configuring models, and
running inference scripts, alongside code snippets and troubleshooting advice.

While several open-source and commercial solutions address parts of this workflow, most depend on
cloud infrastructure or separate services. Projects like Real-Time-Voice-Cloning and Mozilla TTS
excel at local voice synthesis, and Wav2Lip and SyncNet offer speaker-agnostic lip-sync
capabilities. Commercial tools such as Adobe Character Animator or CrazyTalk let users animate
images without code, whereas platforms like Synthesia and D-ID provide end-to-end video creation
online. This cookbook demystifies the underlying algorithms, empowering you to implement a cohesive,
offline solution that you can extend for research or production purposes.

